Constant-round Blind Classical Verification of Quantum Sampling

### 2020-10-27 qpip0.tex
Sync Overleaf with Github

In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients following the approach taken in \cite{FOCS:Mahadev18a}.
The core protocol, $\PiMeasure$, allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
We now try to compose $\PiMeasure$ similarly with our $\QPIP_1$ protocol $\PiSamp$ for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$

A direct composition between $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ which does not provide reasonable completeness or accuracy guarantees.
As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
the client doesn't always obtain measurement outcomes even if the server were honest.
When that happens under the $\BQP$ context, the verifier can simply accept the prover at the cost of some soundness error;
under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
We spend the majority of this section analyzing the soundness of this parallel repetition.

@@

$\PiMeasure$ is a 4-round protocol between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
The verifier chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$. It sends $pk$ to the prover. The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
The verifier must then choose between two options: do a \emph{testing round} or a \emph{Hadamard round}.
In a testing round the verifier can catch cheating provers,
and in a Hadamard round the verifier receives some measurement outcome.
He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.

@@

\begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
\end{lemma}

>>>>

%to create a fully classical delegation protocol for $\BQP$

In this section, we create a delegation protocol for $\SampBQP$ with fully classical clients by adapting the approach taken in \cite{FOCS:Mahadev18a}. In \cite{FOCS:Mahadev18a}, 
Mahadev designed a protocol $\PiMeasure$ (\cref{proto:urmila4}) that allows a $\BQP$ prover to ``commit a state" for a classical verifier to choose a measurement basis and obtain corresponding measurement results.
Composing it with the $\QPIP_1$ protocol for $\BQP$ from \cite{mf16} results in a $\QPIP_0$ protocol for $\BQP$.
In this work, We try to compose $\PiMeasure$ with our $\QPIP_1$ protocol $\PiSamp$ (\cref{ProtoQPIP1}) for $\SampBQP$ in order to obtain a $\QPIP_0$ protocol for $\SampBQP$

A direct composition of $\PiSamp$ and $\PiMeasure$, however, results in $\PiNaive$ (\cref{proto:qpip0_naive}) which does not provide reasonable completeness or accuracy guarantees.
As we will see, this is due to $\PiMeasure$ itself having peculiar and weak guarantees:
the client doesn't always obtain measurement outcomes even if the server were honest.
When that happens under the $\BQP$ context, the verifier can simply accept the prover at the cost of some soundness error;
under our $\SampBQP$ context, however, we must run many copies of $\PiNaive$ in parallel so the verifier can generate its outputs from some copy.
We spend the majority of this section analyzing the soundness of this parallel repetition.

@@

$\PiMeasure$ is a 4-round protocol between a verifier (which corresponds to our client) and a prover (which corresponds to our server).
The verifier (secretly) chooses a string $h$ specifying the measurements he wants to make, and generates keys $pk, sk$ from $h$. It sends $pk$ to the prover. The prover ``commits" to a state $\rho$ of its choice using $pk$ and replies with its commitment $y$.
The verifier must then choose between two options: do a \emph{testing round} or a \emph{Hadamard round}.
In a testing round the verifier can catch cheating provers,
and in a Hadamard round the verifier receives some measurement outcome.
He sends his choice to the prover, and prover replies accordingly. If the verifier chose testing round, he checks the prover's reply against the previous commitment, and rejects if he sees an inconsistency. If the verifier chose Hadamard round, he calculates $M_{XZ}(\rho, h)$ based on the reply.
We now formally describe the interface of $\PiMeasure$ while omitting the implementation details.

@@

\begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating \hannote{defined?} prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$ \hannote{too weak?}, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
\end{lemma}
